%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Tom Sarry}} & Email: \href{mailto:}{tom.sarry@mail.mcgill.ca}\\
  % \href{https://xprilion.com}{Portfolio: xprilion.com} & Mobile:~~~+91-XXX-XXXX-XXX \\
  \href{https://github.com/tomsarry}{Github: ~~~~github.com/tomsarry} \\
  \href{https://www.linkedin.com/in/tom-sarry-5525a8173/}{LinkedIn: ~~linkedin.com/in/tom-sarry-5525a8173} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McGill University}{Montreal, Canada}
      {Bachelor of Science - Computer Science;  GPA: 4.0}{Sept 2019 - April 2022}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Blockchain Systems, Distributed Systems, Networks, Databases, Operating Systems, Artificial Intelligence.}}}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Research Experience:} Collaborated with two McGill professors to submit a paper to the ICSE conference.}}}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Extra Curriculars} Java OOP tutor, Functional Programming mentor.}}}
    \resumeSubheading
      {Université de Montréal}{Montréal, Canada}
      {Masters of Science - Computer Science}{Sept 2022 - Present}
      % TODO: fill when I took the classes :)
      % {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Blockchain Systems, Distributed Systems, Networks, Databases, Operating Systems, Artificial Intelligence }}}
    \resumeSubHeadingListEnd
	    
\vspace{5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{French (Native), English (Fluent), Spanish (Intermediary)}
	\resumeSubItem{Programming Languages}{C++, Go, TypeScript, Bash, JAVA}
	\resumeSubItem{Frameworks}{React, Svelte, Qt}
	\resumeSubItem{Tools}{Git, Docker, Datadogs, PostgresQL, Firebase, MongoDB}
	\resumeSubItem{Platforms}{Linux, Windows}
\resumeSubHeadingListEnd

\vspace{5pt}
\section{Experience}
  \resumeSubHeadingListStart
    % Broadsign
    \resumeSubheading{Broadsign}{Montreal, Canada}
    {Software Engineer Intern}{May 2022 - Aug 2022}
    \resumeItemListStart
        \resumeItem{C++}
          {Maintained performance-critical code used in more than 50,000 advertisement players around the world.}
        \resumeItem{Kafka}
          {Created polling and processing of events in a new microservice used to unify Broadsign's applications.}
        \resumeItem{GTest}
          {Added unit and integration tests, following the TDD paradigm.}
    \resumeItemListEnd

    % Bitstack
    \resumeSubheading
		{Bitstack}{Remote}
		{Softare Developer Intern}{May 2021 - Aug 2021}
		\resumeItemListStart
        \resumeItem{Flutter}
          {Built most screens for a Bitcoin automated savings application.}
        \resumeItem{Dart}
          {Took ownership of multiple core components of the application, such as the user's portfolio graph, with multiple period selection and automated caching for efficiency.}
        \resumeItem{Python / FastAPI}
          {Created a REST API endpoint to generate monthly user statements as PDF for any given period.}
        \resumeItem{i18n}
          {Integrated an i18n translation module and currency formatting for both french and english speaking users.}
        \resumeItem{Websockets}
          {Set up a Websocket connection to retrieve live data about Bitcoin’s price from our third party.}
		\resumeItemListEnd

    % Sweater Planet
    \resumeSubheading
		{Sweater Planet}{Remote}
		{Softare Developer Intern}{Jan 2021 - Apr 2021}
		\resumeItemListStart
        \resumeItem{React (TypeScript)}
          {Built core screens for user-facing and admin panel of the application.}
        \resumeItem{Node (TypeScript)}
          {Developed core micro-services to allow users create and manage their own merchandise store.}
        \resumeItem{Mocha / Chai}
          {Added unit tests to increase code coverage.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{5pt}
\section{Projects}
  \resumeSubHeadingListStart

    % Wasted on Youtube
    \resumeSubheading
		{Wasted on Youtube}{\href{https://github.com/tomsarry/WOYT}{See on github}}
		{Data Processing, React, Go, Docker}{Aug 2020 - Sep 2020}
		\resumeItemListStart
        \resumeItem{Go}
          {Backend to compute the total estimated time spent on Youtube, with the Youtube API and Google Takeout.}
        \resumeItem{Performance}
          {Randomized sampling and multi-threading to decrease API calls duration from 2h30 to 500ms.}
        \resumeItem{React (TypeScript)}
          {Created a web application to allow users to interact easily with the Backend.}
        \resumeItem{Hosting}
          {Hosted this project using Heroku and Netlify, to let anyone enjoy it.}
		\resumeItemListEnd

    % Kattis Scrapper 
    \resumeSubheading{Kattis Scrapper}{\href{https://github.com/tomsarry/kattis-scraper}{See on github}}
    {Web Scraper, Go}{Nov 2022}
    \resumeItemListStart
        \resumeItem{Go}
          {Created a web scrapper for the Kattis website to retrieve the problems solved.}
    \resumeItemListEnd

    % Weather
    \resumeSubheading{Weater}{\href{https://github.com/tomsarry/weather}{See on github}}
    {CLI, Go}{Nov 2022}
    \resumeItemListStart
        \resumeItem{Go}
          {Built a fast CLI weather app to get the weather for any city, used in my Linux environment.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------Awards-----------------
\vspace{5pt}
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
  \item {\textbf{Science Scholarship (x2):} awarded to the top 5\% students in the science faculty at McGill.}
  \item {\textbf{2nd place winner Internet of Things, Codejam Hack}: 300 participants, 40 submissions}
\end{description}

\vspace{5pt}
\section{Hobbies}
\begin{description}[font=$\bullet$]
  \item \textbf{Bitcoin, Lightning Network, Cooking}
  \item \textbf{Long distance running:} Half marathon finisher (x2), currently training for Montreal Marathon.  
\end{description}

\end{document}